%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Tristan Davey Resume
% Author: Tristan Davey
% Repository: https://github.com/tjdavey/cv
%
% Original template author: Debarghya Das (http://debarghyadas.com)
% Original template repository: https://github.com/deedydas/Deedy-Resume
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{tjd-cv}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Tristan Davey}{Software Engineering Leader | Experienced Full Stack Software Engineer}{ \urlstyle{same}\href{http://tristandavey.com}{tristandavey.com} | \href{mailto:tristan@tristandavey.com}{tristan@tristandavey.com} | \href{tel:+61437231991}{+61 437 231 991} | Townsville, Australia
}

\begin{minipage}[t]{1\textwidth}
\section{Summary}
\vspace{\topsep}
\normalfont
\normalsize
\begin{tightemize}
\item Leadership of multiple agile software engineering teams delivering commercial products.
\item 14 years experience in full-stack development in multiple languages, frontend frameworks and embedded platforms.
\item Practical infrastructure and developer operations knowledge.
\item Previous industry experience in compliance-heavy industries, SAAS and hardware startups.
\item Experience in scaling startups and software engineering teams from 3 people to 100+.
\end{tightemize}
\end{minipage}

\hspace{0pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.26\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{James Cook University}
\role{Bachelor of IT with Honours}
\period{2011 | Townsville, Australia}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Leadership}
Agile development processes \textbullet{}
Mentoring \textbullet{}
Team management \textbullet{}
Stakeholder engagement \textbullet{}
Cross-functional collaboration \textbullet{}
Performance management

\vspace{8pt}
\subsection{Programming}
Golang \textbullet{}
Typescript/Javascript \textbullet{}
C \textbullet{}
C++ \textbullet{}
Ruby \textbullet{}
Python \textbullet{}
SQL \textbullet{}
HTML

\vspace{8pt}
\subsection{Frameworks}
React \textbullet{}
Ember \textbullet{}
Rails \textbullet{}
Hapi

\vspace{8pt}
\subsection{Technologies}
Amazon Web Services \textbullet{}
Google Cloud Services \textbullet{}
Docker \textbullet{}
PostgreSQL \textbullet{}
Couchbase \textbullet{}
DynamoDB \textbullet{}
Apache Kafka \textbullet{}
MQTT \textbullet{}
Redis \textbullet{}
Memcached

\vspace{8pt}
\subsection{AI/ML}
LLMs (ChatGPT, Claude, etc) \textbullet{}
Github Copilot \textbullet{}
Cursor \textbullet{}
Junie \textbullet{} 
Rekognition \textbullet{}
OpenCV

\vspace{8pt}
\subsection{Tooling}
Terraform \textbullet{}
Cloudformation \textbullet{}
Serverless \textbullet{}
AWS CDK

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Professional
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Associations}
\vspace{\topsep}
\begin{tightemize}
\item Australian Computer Society
\item Australian Institute of Company Directors
\item Unicode Consortium
\end{tightemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.70\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\rolesubsection{Ranlytics Pty Ltd}{Head of Software Engineering}
\period{May 2019 - January 2025}
\vspace{\topsep}
\begin{tightemize}
\item Developed and validated product concepts with company leadership and customers.
\item Architected software and infrastructure for terabyte scale data ingestion and querying, a near-real time data visualisation and alerting platform, and several unique RF monitoring solutions.
\item Project managed and developed software for embedded RF monitoring devices, backend data processing, internal and external APIs, and frontend user interfaces.
\item Collaborated with electrical engineers, RF engineers, UX consultants, and industrial designers to design, build and validate new products, and refine the manufacturing and quality control of existing products.
\item Led a series of process changes including CI automation, code and infrastructure instrumentation and team cultural changes reducing recurrent service interruptions of core cloud and data products.
\item Created company and team policies, processes and audits to ensure ongoing ISO 9001, ISO 27001, SOC 2, FCC compliance.
\item Recruited and led several teams of software engineers handling employee welfare and counselling, professional development, performance management and team organisation and structure.

\end{tightemize}
\sectionsep

\rolesubsection{SafetyCulture Pty Ltd}{Lead Software Engineer}
\period{June 2012 – February 2019}
\begin{tightemize}
\item Architected, developed, tested and launched web services and web applications for workplace auditing and safety including full-stack development in multiple languages.
\item Built developer operations tooling, including continuous integration and deployment automation for Amazon EC2, Docker and Amazon ECS deployment in a microservice environment.
\item Implemented and automated unit, API and frontend testing; dependency vulnerability management; test coverage monitoring; linting and other quality and security measures.
\item Managed, supervised and mentored of multiple teams of software engineers, quality assurance engineers and product designers using Agile methodologies.
\item Developed and coordinated of work-experience programmes, an internship programme for university students, and Townsville employer brand development and community outreach.
\end{tightemize}
\sectionsep

\rolesubsection{Mojito Solutions}{Web Developer}
\period{June 2011 – June 2012}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Volunteer Roles
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Volunteer Roles}
\vspace{\topsep}
\rolesubsection{Smart Precinct North Queensland}{Company Director}
\period{December 2019 – Ongoing}
\sectionsep

\rolesubsection{DevNQ - NQ Software Development Community}{Chairperson}
\period{June 2016 – Ongoing}
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}
